Can greedy-like heuristics be useful for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization?

### 2020-10-13 doc/paper.tex
sitne izmjene i dodata jedna referenca

	In order to solve this model, we apply a general purpose solver \textsc{Cplex}~\cite{lima2010ibm}.
	\subsection{Constraint programming model} An equivalent CP model was implemented and tested by \textit{IBM ILOG CP Optimizer}~\cite{laborie2018ibm}. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
	\begin{equation}
	\bigvee_{ j=1}^n (a_{ij} \wedge x_j) = 1, \forall p_i \in D(P),
	\end{equation}
	whereas the other constraints and the objective function are the same as in the above ILP model. Note that CP approach works in a branch-and-bound manner employing a constraint propagation and variable domain filtering~\cite{rossi2006handbook}.
	\section{Algorithmic Approaches for solving WOAGP}
	In this section we present the heuristic greedy approaches for solving WOAGP\fxnote{treba li ovdej w.r.t. regulagrid discrtization?} and their hybridization with the exact ILP method. 
	\subsection{Greedy approaches for solving WOAGP}
 Greedy algorithms produce a solution of reasonable quality within a short interval of time and are, in essence, easy to implement. Efficiency of such  heuristic is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one. In order to extend current partial solution, among all candidates (solution components for expansion, that is not-yet-considered guards),  we choose one with the smallest greedy value and add it to the current solution. This procedure is repeating until the current solution becomes complete (i.e., all points from $D(P)$ are covered).

@@

	%  \subsection{Greedy Criterion based on Price-per-Unit}
	Concerning the greedy heuristic for the literature for solving MWSCP ~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristic was based on the following criterion:
	\begin{align}\label{eq:Lovasz}
	g_1(s^{ps}, v_i) = \frac{w_{i}}{ f(s^{ps} \cup \{v_i\})  - f(s^{ps})},
	\end{align}
	where
\begin{equation}\label{eq:sp}
    f(s^{ps}) = \left|\bigcup_{v_i \in s^{ps}} S_i \right|.
    \end{equation}
	This heuristic  also ensures an approximation with $O(\log(n))$ approximation factor.

	\subsubsection{A Novel Greedy Heuristic}
	In this subsection we present a novel greedy criterion. First, we introduce a term  ``incorrect point''. For a point from $D(P)$ we say that it is \textit{incorrect} if it is not covered by any guard from the current partial solution $s^{ps}$. Let us denote by $incorrect_{total}(s^{ps})$ the total number of incorrect points from discretization $D(P)$ w.r.t. $s^{ps}$. Note that
 \begin{equation}\label{eq:incorrect}
 incorrect_{total}(s^{ps}) = |D(P)|-f(s^{ps}),
 \end{equation}

 where $f(s^{ps})$ is defined in (\ref{eq:sp}) and $|D(P)|$ is the cardinality of discretization set. Let $w_{total}$ be the total sum of all weights among all vertices. The greedy function w.r.t. partial solution $s^{ps}$ and candidate guard $v$ is defined as follows.
	\begin{equation}\label{eq:greedyfun2}
    g_2(s^{ps}, v)  =    \frac{\sum_{i \in s^{ps} \cup \{v\}} w_i}{w_{total}}+ \frac{incorrect_{total}(s^{ps}\cup v)}{|D(P)|}.
	\end{equation}

@@

\subsection{A Hybrid of the \textsc{Greedy} and \textsc{Cplex}}
	The performance of \textsc{Cplex}  sooner or later degrades w.r.t. instance size due to the complexity of the problem. On the other hand, in the later stage, there is an increased chance for Greedy to worsen the obtained greedy solution due to an increased number of guards which are similar w.r.t. greedy value. So, it makes sense to combine  partial solutions generated with a Greedy procedure over a few iterations  and only then to make use the \textsc{Cplex} to do the completion of the partial solution. In details, our approach consists of the following steps:
	\begin{enumerate}
		\item Run a Greedy method up to $K$ iterations  to obtain a partial solution $s^{ps}$, where $K$ is a parameter of the algorithm.
		\item Take solution $s^{ps}$ and make it complete by solving a corresponding submodel via \textsc{Cplex}:
		\begin{itemize}
			\item \textsc{Cplex} solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^{ps}$ into the existing ILP  model~(\ref{eq:woagp-min})--(\ref{eq:const-4});
			\item a complete solution $\overline s$ is obtained;
		\end{itemize}
		\item Return $f(\overline s)$.
	\end{enumerate}
    This method is, therefore, called \textsc{Greedy}+\textsc{Cplex}.
	\begin{comment}

@@

 We used two different kind of benchmark sets from~\cite{tomas2006visibility,bajuelos2004partitioning}: 
     \begin{itemize}
     	 \item \emph{MinArea} instances: MinArea includes polygons with a small areas and tiny interior. They present a lower boundary case for the cardinality of set $D(P)$ which means that, beside the polygon vertices,  $D(P)$ contains few additional points.
     	 \item \emph{FAT} instances:  includes polygons of large areas and wide interior. In this case,  a large number of points of regular grid is included into $D(P)$.
     \end{itemize}
     For each benchmark set -- \emph{MinArea} and \emph{FAT} instances -- one $n$-ogon for each $n \in\{8,10,...,200\}$ has been considered and the appropriate discretization is made, which makes 97 instances per each benchmark set. In overall, we have 194 instances. Discretization is performed by using \fxnote{nismo nigdje ubacili, a ovdje bi trebalo CGAL}.

	We included two kind of weights into each of 194  instances:
	\begin{itemize}
		\item \emph{topologically-based related weights} ($W0$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$. Then, we set 
\begin{equation}
w_i := \frac{l_i + l_{i+1}}{2}.
 \end{equation}
 This way of assigning weights is augmented by the fact that if the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$. This implies that the spectrum of camera installed at $v_i$ has to be larger, which again implies that it should be of a higher quality, i.e,. a higher price.
		\item \emph{point-based related weights} ($W1$): For each vertex $v_j$, based on the number of points in $D(P)$ that are visible from $v_j$, we assign prices to each vertex on the following way:
		\begin{equation}
		w_i = n \cdot \frac{|S_i|}{|D(P)|},\ i=1,...,n.
		\end{equation}
    Similarly as in case of $W0$, cameras which cover larger range of points are considered be of a higher spectrum and quality, and thus are more expensive.
	\end{itemize}

@@

     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}. \fxnote{dodati link}
	\subsection{Results and Discussion}
        The following algorithms are included in our computation:
        \begin{itemize}
        	\item  exact approaches: CP and ILP approach. The later is, henceforth, called \textsc{Cplex};
            \item 4 heuristic approaches:
           \begin{itemize}
           	\item two pure greedy methods, guided by $g_1$ and $g_2$, labeled as \textsc{Greedy-1}, \textsc{Greedy-2}, respectively;
            %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
            \item two \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy-1}+\textsc{Cplex} and
            \textsc{Greedy-2}+\textsc{Cplex}.
        \end{itemize}
    \end{itemize}

         Summarized numerical results for each of our 6 variants of our algorithm are displayed
         in Tables~\ref{small_wo} -- \ref{large_w1}. For each table, the average results are reported for each subset of instances grouped w.r.t. a specific kind of instances and a specific weight (97 instances per each group). Each of the tables list the tested algorithms in the first column. Starting with column two,  each of the lines provide detailed statistics for respective algorithm.  The statistics report: the average solution quality ($\overline{|s|}$), the average time ($\overline{t}[s]$) in seconds, the average number of guards which are included in each of the solutions ( $\overline{|g|}$), the number of solutions which match to the optimum solutions (\#optHit), average standard deviation of the obtained solutions w.r.t. optimal solutions ($\sigma(Opt)$), then the number of minimal solutions the algorithm obtained w.r.t. the four heuristics achieved by the respective algorithm (\#hitsMinH) and average standard deviation w.r.t. best (minimal) solutions achieved by the four heuristic algorithms   ($\sigma(MinH)$).  An asterisk in front of a number means that the exact approach  could prove optimality in all cases. Best values among heuristic approaches in each column are bolded.

     \begin{table}[]
     	\centering
     	 \scalebox{0.83}{
     	\begin{tabular}{l|lllllll}    \hline
     		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & *15.93  & 0.152    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 16.04  & 98.215   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\ \hline
     		\textsc{Greedy-1}             & 22.63  & \textbf{0.002}    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
     		\textsc{Greedy-2}          & 19.97  & \textbf{0.002}    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.073    & 21.19     & \textbf{2/97}      & 0.30    & \textbf{57/97}      & \textbf{0.06}     \\
     		   \textsc{Greedy-2+Cplex} & \textbf{18.39}  & 0.004    & \textbf{19.59}     & 0/97      & \textbf{0.26}    & 53/97      & 0.04  \\ \hline
     	\end{tabular}}
        \caption{The results on the benchmark set $MinArea$ for the type of weight $W0$.}\label{small_wo}
     \end{table}

      \begin{table}[]
      	\centering
      	\scalebox{0.83}{
      	\begin{tabular}{l|lllllll} \hline
      		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &  $ \overline{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & *36.03  & 0.003   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Cp}               & *36.03  & 18.953   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\ \hline
      		\textsc{Greedy-1}             & 39.28  & \textbf{0.001}    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
      		\textsc{Greedy-2}          & 40.92  & \textbf{0.001}    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.006    & 19.41     & \textbf{4/97}      & 0.21    & 19/97      & \textbf{0.08}     \\
      		   \textsc{Greedy-2+Cplex} & \textbf{37.31}  & 0.003    & \textbf{19.58}     & 2/97      & \textbf{0.15}    & \textbf{81/97}     & {0.19}   \\ \hline
      	\end{tabular}}
         \caption{The results on the bemchmark set $MinArea$ for the  type of weight $W1$.}\label{small_w1}
      \end{table}

     \begin{table}[]
      \centering
       \scalebox{0.85}{
     	\begin{tabular}{l|lllllll} \hline
     		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & *2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & *2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\ \hline
     		\textsc{Greedy-1}             & 3.39   & 0.35    & 7.81      & 0/97      & 0.09    & 23/97      & 0.05     \\
     		\textsc{Greedy-2}          & 3.52   & \textbf{0.32}    & 6.61      & 2/97      & 0.10    & \textbf{28/97}      & 0.08     \\
     		   \textsc{Greedy-1+Cplex}  & 3.34   & 0.35    & 8.91      & 4/97      & \textbf{0.08}    & 25/97      & \textbf{0.04}     \\
     		   \textsc{Greedy-2+Cplex} & \textbf{3.32}   & 0.33    & \textbf{6.81}      & \textbf{6/97}      & \textbf{0.08}    & 25/97      & \textbf{0.04}  \\ \hline
     	\end{tabular}}
          \caption{The results on the benchmark set $FAT$ for the type of weight $W0$.} \label{large_w0}
     \end{table}

    \begin{table}[]
    	\centering
    	\scalebox{0.85}{
 	  \begin{tabular}{l|lllllll} \hline
 		Alg.           & $\overline{|s|}$ & $\overline{t}[s]$ &   $\overline{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
 		\textsc{Cplex}            & *6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Cp}               & *6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\ \hline
 		\textsc{Greedy-1}             & 6.77   & \textbf{0.31}    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		\textsc{Greedy-2}          & 6.77   & \textbf{0.31}    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		\textsc{Greedy-1+Cplex}  & \textbf{6.73}   & 0.32    & \textbf{6.45}      & \textbf{96/97}     & \textbf{0.01}    & \textbf{96/97}      & \textbf{0.03}     \\
 		\textsc{Greedy-2+Cplex} & 7.42   & \textbf{0.31}    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
 	\end{tabular}}
    \caption{The results on the benchmark set $FAT$ for the type of weight $W1$.}\label{large_w1}
   \end{table}

        From the numerical results, we observe the following conclusions concerning exact solving:
        \begin{itemize}
        	\item  \textsc{Cplex} could solve all solution to prove optimality within a fraction of a second;
        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with significantly more time than the time required from \textsc{Cplex};
        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of Cp degrades significantly, which can be seen  by the respective average runtime and the number of proven optimal solutions found (67/97).
        \end{itemize}
     From the numerical results, we observe the following conclusions concerning heuristic solving:
     \begin{itemize}
     	\item  In case of the instances that include small--area polygons ($MinArea$) and weight $W0$ (Table~(\ref{small_wo})): A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature. In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs the two order of magnitude lower average runtime to finish than the pure greedy methods. The average runtimes of all four heuristic methods are an order of magnitude lower than the average runtime of \textsc{Cplex}. Pure greedy methods deliver solutions of reasonable quality within 20\% of the quality of optimal solutions but needs the time which is 7-8 times lower then the average runtime of \textsc{Cplex}. Although all heuristic methods could not achieve optimal solutions (with the exception of two cases for \textsc{Greedy-1+Cplex} heuristics), the average standard deviation w.r.t. optimal solution is rather small. From last two columns, it is evident that both hybrid variants are more successful, hitting more than a half best solution each, with very small average standard deviation w.r.t. optimal solutions.
     	\item  In case of the instances that include small-area polygons and weight $W1$ (Table~\ref{small_w1}): the best heuristic approach is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones. Note that in 81 cases (out of 91) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches. As it was the case  of the weight $W0$, heuristic methods could not achieve many optimal solutions, but the obtained  average standard deviation w.r.t. optimal solutions is rather small.
     	The results of pure greedy method \textsc{Greedy-1} outperform the results of \textsc{Greedy-2}. These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but need 3 times less runtime. The results of \textsc{Greedy-1} match just in two cases to the optimum.

@@

	\section*{Acknowledgements}
This research is partially supported by Ministry for Scientific and Technological
Development, Higher Education and Information Society, Government
of Republic of Srpska, B\&H under the Project \fxnote{ime projekta}.

>>>>

	In order to solve this model, we apply a general purpose solver \textsc{Cplex}~\cite{lima2010ibm}.
	\subsection{Constraint programming model} An equivalent CP model was implemented and tested by \textit{IBM ILOG CP Optimizer}~\cite{laborie2018ibm}. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
	\begin{equation}
	\bigvee_{ j=1}^n (a_{ij} \wedge x_j) = 1, \forall p_i \in D(P),
	\end{equation}
	whereas the other constraints and the objective function are the same as in the above ILP model. Note that CP approach works in a branch-and-bound manner employing a constraint propagation and variable domain filtering~\cite{rossi2006handbook}.
	\section{Algorithmic Approaches for solving WOAGP}
	In this section we present the heuristic greedy approaches for solving the considered problem and their hybridization with the exact ILP method.
	\subsection{Greedy approaches for solving WOAGP}
 Greedy algorithms produce a solution of reasonable quality within a short interval of time and are, in essence, easy to implement. Efficiency of such  heuristic is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one. In order to extend current partial solution, among all candidates (solution components for expansion, that is not-yet-considered guards),  we choose one with the smallest greedy value and add it to the current solution. This procedure is repeating until the current solution becomes complete (i.e., all points from $D(P)$ are covered).

@@

	%  \subsection{Greedy Criterion based on Price-per-Unit}
	Concerning the greedy heuristic for the literature for solving MWSCP ~\cite{chvatal1979greedy, lovasz1975ratio}, one of the most efficient greedy heuristics was based on the following criterion:
	\begin{align}\label{eq:Lovasz}
	g_1(s^{ps}, v_i) = \frac{w_{i}}{ h(s^{ps} \cup \{v_i\})  -h(s^{ps})},
	\end{align}
	where
\begin{equation}\label{eq:sp}
    h(s^{ps}) = \left|\bigcup_{v_i \in s^{ps}} S_i \right|.
    \end{equation}
	This heuristic  also ensures an approximation with $O(\log(n))$ approximation factor.

	\subsubsection{A Novel Greedy Heuristic}
	In this subsection we present a novel greedy criterion. First, we introduce a term  ``incorrect point''. For a point from $D(P)$ we say that it is \textit{incorrect} if it is not covered by any guard from the current partial solution $s^{ps}$. Let us denote by $incorrect_{total}(s^{ps})$ the total number of incorrect points from discretization $D(P)$ w.r.t. $s^{ps}$. Note that
 \begin{equation}\label{eq:incorrect}
 incorrect_{total}(s^{ps}) = |D(P)|-h(s^{ps}),
 \end{equation}

 where $h(s^{ps})$ is defined in (\ref{eq:sp}) and $|D(P)|$ is the cardinality of discretization set. Let $w_{total}$ be the total sum of all weights among all vertices. The greedy function w.r.t. partial solution $s^{ps}$ and candidate guard $v$ is defined as follows.
	\begin{equation}\label{eq:greedyfun2}
    g_2(s^{ps}, v)  =    \frac{\sum_{i \in s^{ps} \cup \{v\}} w_i}{w_{total}}+ \frac{incorrect_{total}(s^{ps}\cup v)}{|D(P)|}.
	\end{equation}

@@

\subsection{A Hybrid of the \textsc{Greedy} and \textsc{Cplex}}
	The performance of \textsc{Cplex}  sooner or later degrades w.r.t. instance size due to the complexity of the problem. On the other hand, in the later stage, there is an increased chance for Greedy to worsen the obtained greedy solution due to an increased number of guards which are similar w.r.t. greedy value. So, it makes sense to combine  partial solutions generated with a Greedy procedure over a few iterations  and only then to make use the \textsc{Cplex} to do the completion of the partial solution. In details, our approach consists of the following steps:
	\begin{enumerate}
		\item Run a Greedy method up to $K$ iterations  to obtain a partial solution $s^{ps}$, where $K$ is a parameter of the algorithm.
		\item Take solution $s^{ps}$ and make it complete by solving a corresponding submodel via \textsc{Cplex}:
		\begin{itemize}
			\item \textsc{Cplex} solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^{ps}$ into the existing ILP  model~(\ref{eq:woagp-min})--(\ref{eq:const-4});
			\item a complete solution $\overline s$ is obtained;
		\end{itemize}
		\item Return $obj(\overline s)$.
	\end{enumerate}
    This method is, therefore, called \textsc{Greedy}+\textsc{Cplex}.
	\begin{comment}

@@

 We used two different kind of benchmark sets from~\cite{tomas2006visibility,bajuelos2004partitioning}:
     \begin{itemize}
     	 \item \emph{MinArea} instances: MinArea includes polygons with a small areas and tiny interior. They present a lower boundary case for the cardinality of set $D(P)$ which means that, beside the polygon vertices,  $D(P)$ contains few additional points.
     	 \item \emph{FAT} instances:  includes polygons of large areas and wide interior. In this case,  a large number of points of regular grid is included into $D(P)$.
     \end{itemize}
     For each benchmark set -- \emph{MinArea} and \emph{FAT} instances -- one $n$-ogon for each $n \in\{8,10,...,200\}$ has been considered and the appropriate discretization is made, which makes 97 instances per each benchmark set. In overall, we have 194 instances. Discretization is performed by using CGAL \cite{cgal:eb-20b}.

	We included two kind of weights into each of 194  instances:
	\begin{itemize}
		\item \emph{topologically-based related weights} ($W0$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$. Then, we set
\begin{equation}
w_i := \frac{l_i + l_{i+1}}{2}.
 \end{equation}
 This way of assigning weights is augmented by the fact that if the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$. This implies that the spectrum of camera installed at $v_i$ has to be larger, which again implies that it should be of a higher quality, i.e,. a higher price.
		\item \emph{point-based related weights} ($W1$): For each vertex $v_i$, based on the number of points in $D(P)$ that are visible from $v_i$, we assign prices to each vertex on the following way:
		\begin{equation}
		w_i = n \cdot \frac{|S_i|}{|D(P)|},\ i=1,...,n.
		\end{equation}
    Similarly as in case of $W0$, cameras which cover larger range of points are considered be of a higher spectrum and quality, and thus are more expensive.
	\end{itemize}

@@

     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}. \fxnote{dodati link}
	\subsection{Results and Discussion}
        The following algorithms are included in our computation:
        \begin{itemize}
        	\item  exact approaches: CP and ILP approach. The latter is, henceforth, called \textsc{Cplex};
            \item 4 heuristic approaches:
           \begin{itemize}
           	\item two pure greedy methods, guided by $g_1$ and $g_2$, labeled as \textsc{Greedy-1}, \textsc{Greedy-2}, respectively;
            %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
            \item two \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy-1}+\textsc{Cplex} and
            \textsc{Greedy-2}+\textsc{Cplex}.
        \end{itemize}
    \end{itemize}

         Summarized numerical results for each of our 6 variants of our algorithm are displayed
         in Tables~\ref{small_wo} -- \ref{large_w1}. For each table, the average results are reported for each subset of instances grouped w.r.t. a specific kind of instances and a specific weight (97 instances per each group). Each of the tables list the tested algorithms in the first column. Starting with column two,  each of the lines provide detailed statistics for respective algorithm.  The statistics report: the average solution quality ($\overline{obj}$), the average time ($\overline{t}[s]$) in seconds, the average number of guards which are included in each of the solutions ( $\overline{|g|}$), the number of solutions which match to the optimum solutions (\#optHit), average standard deviation of the obtained solutions w.r.t. optimal solutions ($\sigma(Opt)$), then the number of minimal solutions the algorithm obtained w.r.t. the four heuristics achieved by the respective algorithm (\#hitsMinH) and average standard deviation w.r.t. best (minimal) solutions achieved by the four heuristic algorithms   ($\sigma(MinH)$).  An asterisk in front of a number means that the exact approach  could prove optimality in all cases. Best values among heuristic approaches in each column are bolded.

     \begin{table}[]
     	\centering
     	 \scalebox{0.83}{
     	\begin{tabular}{l|lllllll}    \hline
     		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & *15.93  & 0.152    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 16.04  & 98.215   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\ \hline
     		\textsc{Greedy-1}             & 22.63  & \textbf{0.002}    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
     		\textsc{Greedy-2}          & 19.97  & \textbf{0.002}    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.073    & 21.19     & \textbf{2/97}      & 0.30    & \textbf{57/97}      & \textbf{0.06}     \\
     		   \textsc{Greedy-2+Cplex} & \textbf{18.39}  & 0.004    & \textbf{19.59}     & 0/97      & \textbf{0.26}    & 53/97      & 0.04  \\ \hline
     	\end{tabular}}
        \caption{The results on the benchmark set $MinArea$ for the type of weight $W0$.}\label{small_wo}
     \end{table}

      \begin{table}[]
      	\centering
      	\scalebox{0.83}{
      	\begin{tabular}{l|lllllll} \hline
      		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &  $ \overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & *36.03  & 0.003   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Cp}               & *36.03  & 18.953   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\ \hline
      		\textsc{Greedy-1}             & 39.28  & \textbf{0.001}    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
      		\textsc{Greedy-2}          & 40.92  & \textbf{0.001}    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.006    & 19.41     & \textbf{4/97}      & 0.21    & 19/97      & \textbf{0.08}     \\
      		   \textsc{Greedy-2+Cplex} & \textbf{37.31}  & 0.003    & \textbf{19.58}     & 2/97      & \textbf{0.15}    & \textbf{81/97}     & {0.19}   \\ \hline
      	\end{tabular}}
         \caption{The results on the bemchmark set $MinArea$ for the  type of weight $W1$.}\label{small_w1}
      \end{table}

     \begin{table}[]
      \centering
       \scalebox{0.85}{
     	\begin{tabular}{l|lllllll} \hline
     		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ &\#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & *2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & *2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\ \hline
     		\textsc{Greedy-1}             & 3.39   & 0.35    & 7.81      & 0/97      & 0.09    & 23/97      & 0.05     \\
     		\textsc{Greedy-2}          & 3.52   & \textbf{0.32}    & 6.61      & 2/97      & 0.10    & \textbf{28/97}      & 0.08     \\
     		   \textsc{Greedy-1+Cplex}  & 3.34   & 0.35    & 8.91      & 4/97      & \textbf{0.08}    & 25/97      & \textbf{0.04}     \\
     		   \textsc{Greedy-2+Cplex} & \textbf{3.32}   & 0.33    & \textbf{6.81}      & \textbf{6/97}      & \textbf{0.08}    & 25/97      & \textbf{0.04}  \\ \hline
     	\end{tabular}}
          \caption{The results on the benchmark set $FAT$ for the type of weight $W0$.} \label{large_w0}
     \end{table}

    \begin{table}[]
    	\centering
    	\scalebox{0.85}{
 	  \begin{tabular}{l|lllllll} \hline
 		Alg.           & $\overline{obj}$ & $\overline{t}[s]$ &   $\overline{|g|}$ & \#optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
 		\textsc{Cplex}            & *6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Cp}               & *6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\ \hline
 		\textsc{Greedy-1}             & 6.77   & \textbf{0.31}    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		\textsc{Greedy-2}          & 6.77   & \textbf{0.31}    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		\textsc{Greedy-1+Cplex}  & \textbf{6.73}   & 0.32    & \textbf{6.45}      & \textbf{96/97}     & \textbf{0.01}    & \textbf{96/97}      & \textbf{0.03}     \\
 		\textsc{Greedy-2+Cplex} & 7.42   & \textbf{0.31}    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
 	\end{tabular}}
    \caption{The results on the benchmark set $FAT$ for the type of weight $W1$.}\label{large_w1}
   \end{table}

        From the numerical results, we observe the following conclusions concerning exact solving:
        \begin{itemize}
        	\item  \textsc{Cplex} could solve all solution to prove optimality within a fraction of a second;
        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with significantly more time than the time required from \textsc{Cplex};
        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of \textsc{Cp} degrades significantly, which can be seen  by the respective average runtime and the number of proven optimal solutions found (67/97).
        \end{itemize}
     From the numerical results, we observe the following conclusions concerning heuristic solving:
     \begin{itemize}
     	\item  In case of the instances that include small--area polygons ($MinArea$) and weight $W0$ (Table~(\ref{small_wo})): A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature. In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs the two order of magnitude lower average runtime to finish than the pure greedy methods. The average runtimes of all four heuristic methods are an order of magnitude lower than the average runtime of \textsc{Cplex}. Pure greedy methods deliver solutions of reasonable quality within 20\% of the quality of optimal solutions but needs the time which is 7-8 times lower then the average runtime of \textsc{Cplex}. Although all heuristic methods could not achieve optimal solutions (with the exception of two cases for \textsc{Greedy-1+Cplex} heuristics), the average standard deviation w.r.t. optimal solution is rather small. From last two columns, it is evident that both hybrid variants are more successful, hitting more than a half best solution each, with very small average standard deviation w.r.t. optimal solutions.
     	\item  In case of the instances that include small-area polygons and weight $W1$ (Table~\ref{small_w1}): the best heuristic approach is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones. Note that in 81 cases (out of 97) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches. As it was the case  of the weight $W0$, heuristic methods could not achieve many optimal solutions, but the obtained  average standard deviation w.r.t. optimal solutions is rather small.
     	The results of pure greedy method \textsc{Greedy-1} outperform the results of \textsc{Greedy-2}. These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but need 3 times less runtime. The results of \textsc{Greedy-1} match just in two cases to the optimum.

@@

	\section*{Acknowledgements}
This research is partially supported by Ministry for Scientific and Technological
Development, Higher Education and Information Society, Government
of Republic of Srpska, B\&H under the Project ``Development of artificial intelligence methods for solving computer biology problems".
